A Two-Infall Star Formation History with Outflows and Radial Migration

### 2024-08-23 src/tex/ms.tex

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}

@@

@@

@@

\todo{Copied from last paper.} First proposed by \citet{Chiappini1997-TwoInfall}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
\end{equation}
% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{chiappini_chemical_1997,spitoni_galactic_2020,spitoni_apogee_2021}. $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and their ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
\begin{equation}
    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
\end{equation}
Following \citet{bland-hawthorn_galaxy_2016}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
We note that most previous studies which use the two-infall model \citep[e.g.][]{chiappini_chemical_1997,matteucci_new_2006,matteucci_effect_2009,spitoni_galactic_2019} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance. We adopt radially-dependent outflows as in \citetalias{johnson_stellar_2021} (see their Section 2.4 for details) for all our SFHs, including two-infall. We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.

>>>>

% Author list
\author[0000-0003-3781-0747]{Liam O.\ Dubay}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0001-7258-1834]{Jennifer A.\ Johnson}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
\author[0000-0002-6534-8783]{James W.\ Johnson}
\affiliation{Observatories of the Carnegie Institution for Science, 813 Santa Barbara St., Pasadena CA 91101, USA}
\affiliation{\osuaffil}
\affiliation{\ccappaffil}
% \author[0000-0001-7775-7261]{David H. Weinberg}
\author{coauthors}

@@

The two-infall model has long been proposed to explain the high- and low-$\alpha$ sequences observed in the Milky Way disk.

@@

\begin{table*}
    \centering
    \caption{Yields.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table*}

@@

\todo{Copied from last paper.} First proposed by \citet{chiappini_chemical_1997}, this model parameterizes the infall rate as two successive, exponentially declining bursts to explain the origin of the high- and low-$\alpha$ disk populations:
\begin{equation}
    \label{eq:twoinfall-ifr}
    f_{\rm TI}(t|R_{\rm gal}) = N_1(R_{\rm gal}) e^{-t/\tau_1} + N_2(R_{\rm gal}) e^{-(t-t_{\rm on})/\tau_2},
\end{equation}
% In this model, the first infall produces the thick disk and the second infall produces the thin disk. 
where $\tau_1=1$ Gyr and $\tau_2=4$ Gyr are the exponential timescales of the first and second infall, respectively, and $t_{\rm on}=4$ Gyr is the onset time of the second infall \citep[based on typical values in, e.g.,][]{chiappini_chemical_1997,spitoni_galactic_2020,spitoni_apogee_2021}. $N_1$ and $N_2$ are the normalizations of the first and second infall, respectively, and their ratio $N_2/N_1$ is calculated so that the thick-to-thin-disk surface density ratio $f_\Sigma(R)=\Sigma_2(R)/\Sigma_1(R)$ is given by
\begin{equation}
    f_\Sigma(R) = f_\Sigma(0) e^{R(1/R_2 - 1/R_1)}.
\end{equation}
Following \citet{bland-hawthorn_galaxy_2016}, we adopt values for the thick disk scale radius $R_1=2.0$ kpc, thin disk scale radius $R_2=2.5$ kpc, and $f_\Sigma(0)=0.27$.
We note that most previous studies which use the two-infall model \citep[e.g.][]{chiappini_chemical_1997,matteucci_new_2006,matteucci_effect_2009,spitoni_galactic_2019} do not consider gas outflows and instead adjust the nucleosynthetic yields to reproduce the solar abundance. We adopt radially-dependent outflows as in \citetalias{johnson_stellar_2021} (see their Section 2.4 for details) for all our SFHs, including two-infall. We discuss the implications of this difference in Section \ref{sec:two-infall-discussion}.

The star formation law follows a single power-law prescription: $\dot\Sigma_\star\propto\Sigma_g^N$, with $N=1.5$ following \citet{kennicutt_global_1998}. Previous work with this GCE model \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} assumed a three-component power-law, but we adopt a simpler prescription to allow for a more direct comparison with previous two-infall studies \citep[e.g.,][]{spitoni_remind_2024}. In detail, we calculate the star formation efficiency (SFE) timescale $\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$ according to the following:
\begin{equation}
    \label{eq:sf-law}
    \tau_\star = 
    \begin{cases}
        \epsilon(t) \tau_{\rm mol}(t),   & \Sigma_g \ge \Sigma_{g,0} \\
        \epsilon(t) \tau_{\rm mol}(t) \Big(\frac{\Sigma_g}{\Sigma_{g,0}}\Big)^{-1/2}, & \Sigma_g < \Sigma_{g,0}
    \end{cases}
\end{equation}
where $\Sigma_{g,0} = 10^8\,{\rm M}_\odot\,{\rm kpc}^{-2}$ and $\tau_{\rm mol}(t)=\tau_{\rm mol,0}(t/t_0)^\gamma$ with $\gamma=1/2$ and $\tau_{\rm mol,0}=2$ Gyr. Previous two-infall studies \citep[e.g.,][]{nissen_high-precision_2020} have adopted a higher SFE during the first infall epoch than during the second, which we emulate through the pre-factor $\epsilon$:
\begin{equation}
    \label{eq:sfe-prefactor}
    \epsilon(t) = 
    \begin{cases}
        0.5, & t < t_{\rm on} \\
        1.0, & t \ge t_{\rm on}.
    \end{cases}
\end{equation}
\todo{Talk about the implications of this prefactor or reference a future section which discusses this.}
